Online learning apps from the learning cycle perspective: recent advances and best practices

### 2023-04-28 review_learning_dashboards_paper/paper.Rmd
Update paper.rmd

# Introduction

@@

1. Engagement.

Various definitions of student engagement exist. For instance, @hu2008 understand engagement as "the amount of effort dedicated to educational activities that bring out ideal performance". @lewis2011 see engagement as "the extent to which learners’ thoughts, feelings, and activities are actively involved in learning".

@@

2. Exploration.

The exploration phase is exemplified in @bybee2006 through experimental activities, preliminary investigation or using prior knowledge to generate new outcomes. Student activities encompass e.g. stating and testing predictions and hypotheses, trying alternatives and generating new ideas. Depending on the subject, such activities can be implemented online through interactive applications with manipulatives (e.g. varying input parameters producing another output), simulations, and scenario-based exploration. These "hands-on" experience has been shown to enhance learning success in the literature, see @meylani2015. It is also connected to experiential learning (see @morris2020), where concrete experience is at core of the learning process.

3. Explanation.

As @bybee2006, this stage consists of providing new concepts or skills which serve as theoretical basis for solving the stated problem or explaining observed phenomena. In a purely online setting, where the instructor can not adapt to learning preferences of the learners, different learning preferences should be taken into account. @meylani2015 reviews works, where adding additional media contributed to learning success. Learners should have a palette of materials to acquire understanding of new concepts (as diagrams, videos, text-based materials) as @Katsaris2021. Cite more learning styles in e-learning.

4. Elaboration

As @bybee2006, elaboration enhances deeper and broader understanding and application of new skills. We interpret this stage also as the possibility for students to intensively exercise and gain routinized skills in solving problems associated with new concepts. Also, in asynchronous online learning, where direct instructor feedback is not available, a self-testing possibility with direct feedback should be provided as @meylani2015. To engage students more in exercising new concepts and attaining routinized skills, gamified learning actovities can be used. As noted in @demmese2020, such gamified activities can aid routine practice motivating to solve more exercises.

5. Evaluation

In this phase, ability assessment and the evaluation of student progress takes place. In online format, individual ability assessment is realized through quizzes with an end score. @meylani2015 points out the importance of self-monitoring in an online framework. An overview of completed activities and attained test scores can be implemented in form of learning analytics dashboard, which have been shown to enable learners to making informed decisions (@susnjak2022).

6. Evolution.

Evolve stage includes improving e-learning environment based on direct feedback, questionnaire (as e.g. system usability scale, @lewis2018) and learning analytics and adding personalized features. @meylani2015 stresses the importance of providing a form of learner control over the available online resources. Based on previous learning paths, an individual recommendation for each learner might nehance learning success. As noted in @Katsaris2021 personalized e-learning environments adapting to individual learning preferences are at rise. They have the potential to support individual learning process optimally. For instance, @fatahi2019 propose adaptation of e-learning environments based on emotion and personality. @khamparia2020 review the methodologies, how e-learning adaptation is realized based on automatic assessment of learning styles and point out an overall utility for learners success.

@@

# Methods

## Searching and filtering the recent works on online learning

@@

@@

for (i in 1:length(keyword_texts$name)){
  keyword_texts[i,2]<-as.character(paste(readLines(paste0(keyword_texts$name[[i]],".txt")),collapse=" "))
}
mydfm2<-make_dfm(keyword_texts$description)
keywords<-list()

@@

@@

# Literature {-}

>>>>

## Introduction {-}

@@

**Engagement.**
Various definitions of student engagement exist. For instance, @hu2008 understand engagement as "the amount of effort dedicated to educational activities that bring out ideal performance". @lewis2011 see engagement as "the extent to which learners’ thoughts, feelings, and activities are actively involved in learning".

@@

**Exploration.**
The exploration phase is exemplified in @bybee2006 through experimental activities, preliminary investigation or using prior knowledge to generate new outcomes. Student activities encompass e.g. stating and testing predictions and hypotheses, trying alternatives and generating new ideas. Depending on the subject, such activities can be implemented online through interactive applications with manipulatives (e.g. varying input parameters producing another output), simulations, and scenario-based exploration. These "hands-on" experience has been shown to enhance learning success in the literature, see @meylani2015. It is also connected to experiential learning (see @morris2020), where concrete experience is at core of the learning process.

**Explanation.**
As @bybee2006, this stage consists of providing new concepts or skills which serve as theoretical basis for solving the stated problem or explaining observed phenomena. In a purely online setting, where the instructor can not adapt to learning preferences of the learners, different learning preferences should be taken into account. @meylani2015 reviews works, where adding additional media contributed to learning success. Learners should have a palette of materials to acquire understanding of new concepts (as diagrams, videos, text-based materials) as @Katsaris2021. Cite more learning styles in e-learning.

**Elaboration**
As @bybee2006, elaboration enhances deeper and broader understanding and application of new skills. We interpret this stage also as the possibility for students to intensively exercise and gain routinized skills in solving problems associated with new concepts. Also, in asynchronous online learning, where direct instructor feedback is not available, a self-testing possibility with direct feedback should be provided as @meylani2015. To engage students more in exercising new concepts and attaining routinized skills, gamified learning actovities can be used. As noted in @demmese2020, such gamified activities can aid routine practice motivating to solve more exercises.

**Evaluation**
In this phase, ability assessment and the evaluation of student progress takes place. In online format, individual ability assessment is realized through quizzes with an end score. @meylani2015 points out the importance of self-monitoring in an online framework. An overview of completed activities and attained test scores can be implemented in form of learning analytics dashboard, which have been shown to enable learners to making informed decisions (@susnjak2022).

**Evolution.**
Evolve stage includes improving e-learning environment based on direct feedback, questionnaire (as e.g. system usability scale, @lewis2018) and learning analytics and adding personalized features. @meylani2015 stresses the importance of providing a form of learner control over the available online resources. Based on previous learning paths, an individual recommendation for each learner might nehance learning success. As noted in @Katsaris2021 personalized e-learning environments adapting to individual learning preferences are at rise. They have the potential to support individual learning process optimally. For instance, @fatahi2019 propose adaptation of e-learning environments based on emotion and personality. @khamparia2020 review the methodologies, how e-learning adaptation is realized based on automatic assessment of learning styles and point out an overall utility for learners success.

@@

## Methods {-}

### Searching and filtering the recent works on online learning {-}

@@

### Fiting keyATM {-}

@@

for (i in 1:length(keyword_texts$name)){
  keyword_texts[i,2]<-as.character(paste(readLines(paste0("5E/",keyword_texts$name[[i]],".txt")),collapse=" "))
}
mydfm2<-make_dfm(keyword_texts$description)
keywords<-list()

@@

### Exploring the interrelations between topics {-}

@@

## Literature {-}
